Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-02-13 MCQMC2022ChallengesQMCSoftwareArticle.tex
2023 Mac 14 Updates

\subsection{Integrands and Variable Transformations} The original integral or expectation arising from the application is defined in terms of the integrand, $g$, and the non-negative weight, $\lambda$.  For example,
\begin{itemize}
	\item $g$ may represent the discounted payoff of a financial derivative and $\lambda$ be the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},

	\item  $g$ may represent the velocity of flow at a point in rock and $\lambda$ is the PDF of the porosity field , or

>>>>

\subsection{Integrands and Variable Transformations} The original integral or expectation arising from the application is defined in terms of the integrand, $g$, and the non-negative weight, $\lambda$.  For example,
\begin{itemize}
	\item $g$ is the discounted payoff of a financial derivative and $\lambda$ be the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},

	\item  $g$ is the velocity of a fluid at a point in rock with a random porosity field whose discretized PDF is $\lambda$, or
